Efficient and Effective Metric Space Indexing for Complete Record Linkage

### 2017-11-20 paper.tex
Update on Overleaf.

\smallskip
\textbf{Traditional  blocking:}
In the traditional blocking technique records are blocked using hand selected keys as described in \cite{Chr12b}. The keys are chosen with the intention of giving the best possible results for the dataset. Multiple blocking keys are commonly used to address the problem of missing and erroneous values preventing matches from being found. Often the choice of blocking keys requires intimate knowledge of the domain and of the records being linked.
fucky fuck fuck.

\smallskip
\textbf{LSH-MinHash:}
The LSH-minhash algorithm used has three tuning parameters:
\emph{shingle size}, $l_{ss}$, the \emph{band size}, $l_{bs}$, and the
\emph{number of bands}, $l_{nb}$.
These are explained in the following algorithm description which follows a standard LSH approach [CITATION].
Using this approach, each record drawn from a set of records is placed in a \emph{LSH-MinHash} data structure.
To do this, for each record, firstly all the fields of the record are turned into strings and 
concatenated. Next the strings are \emph{shingled} into a set of
n-grams (sub-strings of length $n$) according to the $l_{ss}$
parameter (i.e.\ $n = l_{ss}$). Next a set of randomly, 
deterministically generated hash functions are applied to each of the
sets of n-grams and the smallest (the minhash) of each application is
added to a signature. The number of hashes used and thus the size of
the signature is set to $l_{nb} \times l_{bs}$.
Lastly the signature is divided into $l_{nb}$ segments and the elements from the band are hashed again to create a number of keys.
The original record is added to a hashmap associated with each of the keys. 
We we will evaluate the performance of LSH based blocking with regard to the three parameters $l_{ss}$, $l_{bs}$ and $l_{nb}$ in
Sect.~\ref{sec-exp}.

To perform linkage the following procedure is followed: for each query, the value is hashed using the procedure described above and the union of the set of values found for all hashes in the hashmap are returned. These are then be filtered by performing distance calculations on the results to eliminate false positives.

@@

\begin{table}[t]
\caption{Characteristics of data sets used in the experiments.}
 \label{table-datasets}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{cccc}
  \hline\noalign{\smallskip}
  Data set~ & ~Number of~ & ~Number of true~ & Attributes used \\
  name(s)  & records  & matching pairs & for traditional blocking \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA  & 1,295 & 17,184 & many-many & publication-publication\\
  NCVR  & ~448,134~ & ~148,036~ & 1:1  & voter-voter\\
  Isle of Skye & 32,567 & 2,900 & 1:1 * b\\
  Kilmarnock  & 70,852 & 8,300 & 1:1\\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

@@

>>>>

\smallskip
\textbf{Traditional  blocking:}
In the traditional blocking technique records are blocked using hand selected keys as described in \cite{Chr12b}. The keys are chosen with the intention of giving the best possible results for the dataset. Multiple blocking keys are commonly used to address the problem of missing and erroneous values preventing matches from being found. Often the choice of blocking keys requires intimate knowledge of the domain and of the records being linked.

\smallskip
\textbf{LSH-MinHash:}
The LSH-minhash algorithm used has three tuning parameters:
\emph{shingle size}, $l_{ss}$, the \emph{band size}, $l_{bs}$, and the
\emph{number of bands}, $l_{nb}$.
These are explained in the following algorithm description which follows a standard LSH approach \cite{Ind98}.
Using this approach, each record drawn from a set of records is placed in a \emph{LSH-MinHash} data structure.
To do this, for each record, firstly all the fields of the record are turned into strings and 
concatenated. Next the strings are \emph{shingled} into a set of
n-grams (sub-strings of length $n$) according to the $l_{ss}$
parameter (i.e.\ $n = l_{ss}$). Next a set of randomly, 
deterministically generated hash functions are applied to each of the
sets of n-grams and the smallest (the minhash) of each application is
added to a signature. The number of hashes used and thus the size of
the signature is set to $l_{nb} \times l_{bs}$.
Lastly the signature is divided into $l_{nb}$ bands and the values  from each band are hashed again to create a number of keys.
The original record is added to a map associated with each of the keys.

To perform linkage the following procedure is followed: for each query, the value is hashed using the procedure described above and the union of the set of values found for all hashes in the map are returned. These are then filtered by performing distance calculations on the results to eliminate false positives.

@@

\begin{table}[t]
\caption{Characteristics of data sets used in the experiments.}
 \label{table-datasets}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{ccccc}
  \hline\noalign{\smallskip}
  Data set~ & ~Number of~ & ~Number of true~ & ~Linkage~ & ~Entities\\
  name(s)  & records  & matching pairs & type & linked \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA  & 1,295 & 17,184 & many-many & publication-publication\\
  NCVR  & ~448,134~ & ~148,036~ & 1:1  & voter-voter\\
  Isle of Skye & 32,567 & 2,900 & 1:1 & birth-death\\
  Kilmarnock  & 70,852 & 8,300 & 1:1 & birth-death\\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

@@

FFFXXXTTT
We we will evaluate the performance of LSH based blocking with regard to the three parameters $l_{ss}$, $l_{bs}$ and $l_{nb}$ in
Sect.~\ref{sec-exp}.
